Semi-supervised low-rank logistic regression for high-dimensional neuroimaging data

### 2015-05-30 paper_nips/paper.tex
Add a comment on analysis and synthesis and tied weights

where $\mathbf{x \in \mathbb{R}^{d}}$ denotes the vector of $d=79{,}941$
voxel values from each
rest map,
$\mathbf{z \in \mathbb{R}^{n}}$ is the $n$\suggestremove{ hidden dimensions 
(i.e.,
distributed neural activity patterns)}
\suggestadd{-dimensional hidden state}, and 
$\mathbf{x' \in \mathbb{R}^{d}}$
is the reconstruction vector of the original activity map
from the hidden variables. 
% XXX use bold letters for vectors and matrices
Further, $\mathbf{W_0}$ denotes the weight matrix that
transforms
from input space into the hidden space (encoder),
$\mathbf{W_1}$ is the weight matrix for back-projection
from the hidden variables to the
output space (decoder).
$\mathbf{b_0}$ and $\mathbf{b_1}$ are bias vectors.
Note that $\mathbf{W_0}$ and $\mathbf{W_1}$ are tied,
$\mathbf{W_0} = \mathbf{W_1^T}$.
The optimal model parameters $\mathbf{W_0, b_0, b_1}$ are found by
minimizing the expected squared reconstruction error

\begin{equation*}
  \mathbb E\left[{\mathcal{L_{AE}}}(\mathbf{x})\right] = %
  \mathbb E\left[\| \mathbf{x} - f_{AE}(\mathbf{x}) \|^2\right],
\end{equation*}
with \(f_{AE}(\mathbf x) = %
\mathbf{W_1}(\mathbf{W_0}\mathbf{x} + \mathbf{b_0}) + \mathbf{b_1}\)
the autoencoder.
% XXX Michael: I don't know to what extent the following makes sense or is
% XXX correct, so I am commenting it
%% This reconstruction error criterion equates with
%% maximizing a lower bound on the mutual information between
%% input and the learned representation.
Nonlinearities were not applied to the
activations in the first layer.

\paragraph{Reduced-rank logistic regression.}
Lossy compression by a low-dimensional bottleneck
is also imposed by the first layer of the low-rank
multinomial logistic regression.
It gives the probability of an input $\mathbf{x}$ to belong
to a class $i \in \mathbb{N}$

>>>>

where $\mathbf{x \in \mathbb{R}^{d}}$ denotes the vector of $d=79{,}941$
voxel values from each
rest map,
$\mathbf{z \in \mathbb{R}^{n}}$ is the $n$\suggestremove{ hidden dimensions 
(i.e.,
distributed neural activity patterns)}
\suggestadd{-dimensional hidden state}, and 
$\mathbf{x' \in \mathbb{R}^{d}}$
is the reconstruction vector of the original activity map
from the hidden variables. 
% XXX use bold letters for vectors and matrices
Further, $\mathbf{W_0}$ denotes the weight matrix that
transforms
from input space into the hidden space (encoder),
$\mathbf{W_1}$ is the weight matrix for back-projection
from the hidden variables to the
output space (decoder).
$\mathbf{b_0}$ and $\mathbf{b_1}$ are bias vectors.
The optimal model parameters $\mathbf{W_0, b_0, b_1}$ are found by
minimizing the expected squared reconstruction error

\begin{equation*}
  \mathbb E\left[{\mathcal{L_{AE}}}(\mathbf{x})\right] = %
  \mathbb E\left[\| \mathbf{x} - f_{AE}(\mathbf{x}) \|^2\right],
\end{equation*}
with \(f_{AE}(\mathbf x) = %
\mathbf{W_1}(\mathbf{W_0}\mathbf{x} + \mathbf{b_0}) + \mathbf{b_1}\)
the autoencoder.
% XXX Michael: I don't know to what extent the following makes sense or is
% XXX correct, so I am commenting it
%% This reconstruction error criterion equates with
%% maximizing a lower bound on the mutual information between
%% input and the learned representation.
\suggestadd{
Here we choose $\mathbf{W_0}$ and $\mathbf{W_1}$ to be tied, i.e.
$\mathbf{W_0} = \mathbf{W_1^T}$. In particular, this means that the weights
learned are forced to take a two-fold function: That of \textit{analysis} 
and that of \textit{synthesis}. Whereas the first layer \textit{analyzes}
the data in order to obtain the cleanest latent representation, the second
layer represents building blocks from which to \textit{synthesize} the data
using the latent activations. Tying these functionalities makes the analysis
side interpretable and pulls all non-zero singular values towards 1. 
Nonlinearities were not applied to the
activations in the first layer.
}
\paragraph{Reduced-rank logistic regression.}
Lossy compression by a low-dimensional bottleneck
is also imposed by the first layer of the low-rank
multinomial logistic regression.
It gives the probability of an input $\mathbf{x}$ to belong
to a class $i \in \mathbb{N}$
